Outline--Draft JCP format for: Reactive Force Field for Solid Oxides Containing Lanthanum

### 2019-08-20 Paper/paper.tex
Updates from Overleaf
fixed typos

The parametrization of the force field was performed using various stages, and it started with known parameters for C, H, O, S, Fe, and Cr from a previous study of hydrocarbon oxidation on pyrite--covered Cr$_2$O$_3$; \cite{shin_development_2015} and for Ca from a previous study of calcium oxyde hydration. \cite{manzano_hydration_2012}

@@

\begin{figure}[hbtp]
\centering
\includegraphics[scale=1]{three-La-eos.pdf}
\caption{Calculated equations of state corresponding to crystalline La in hexagonal (top), fcc (middle), and bcc (bottom) forms.}
\label{fig:laeos}
\end{figure}

>>>>

The parametrization of the force field was performed using various stages, and it started with known parameters for C, H, O, S, Fe, and Cr from a previous study of hydrocarbon oxidation on pyrite--covered Cr$_2$O$_3$; \cite{shin_development_2015} and for Ca from a previous study of calcium oxide hydration. \cite{manzano_hydration_2012}

@@

\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.5]{Paper/images/LaEoS.png}
\caption{Calculated equations of state corresponding to crystalline La in hexagonal (top), fcc (middle), and bcc (bottom) forms.}
\label{fig:laeos}
\end{figure}
